Proportional multi-state multiple-cohort life table model

### 2018-04-09 MSLT/MSLTdoc.Rmd
Figure labels too far from figures and not showing

#The work in this document requires the following packages (code, rmarkdown and citing packages):
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
require(png)

```
# Introduction

>>>>

#The work in this document requires the following packages (code, rmarkdown and citing packages):
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
```
# Introduction
